---
title: "Add-ons Survey"
author: "Ben Miroglio"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true 
---

<style>
body {
margin-top: 50px;
}
</style>



## Background

This survey was inspired by the chart below, which shows (for all **add-on users**) the distribution of the number of days before a user installed their first add-on. Original re:dash query is [here](https://sql.telemetry.mozilla.org/queries/51128/source#137165). 

```{r, echo=F}
htmltools::includeHTML("./html/days_install.html")
```

The above chart shows that nearly 50% of add-ons users installed their first add-on on the same day their Firefox profile was created, which is closely tied with the Firefox installation date. This implies that most of the new add-on users we see knew exactly what they wanted upon downloading Firefox. We suspect that these users are, in fact, **existing** Firefox users that got new hardware and promptly configured Firefox to their liking on the first session. This occurrence is not identifiable using telemetry, which is why we administered a survey.

---

## Design

We can survey Firefox users using the [Heartbeat](https://wiki.mozilla.org/Firefox/Shield/Heartbeat) service, targeting those with the following characteristics:

* locale of `en-US`, `en-AU`, `en-CA`, `en-GB`, `en-NZ` or `en-ZA`
* version >= `59.0`
* channel = `release`
* 1+ non-system add-ons
* profile created in April, 2018

The survey was distributed on May 11th, 2018 and obtained 990 responses.

---

## Results

This section contains a subset of survey questions. All questions can be found on [Survey Gizmo's dashboard](https://qsurvey.mozilla.com/r/28049_5afdf4ec53d526.64707167).

#### TL;DR

* **40%** of respondents said they were installing Firefox on a new computer
* **80%** said they installed extensions within an hour of installing Firefox
    + 68% (immediately) + 12% (within an hour)
* **94%** said they've used the extensions before
    + 78% (in Firefox) + 16% (in a different browser)

---

#### Detailed Results


```{r, echo=F}
htmltools::includeHTML('./html/addons-survey.html')
```


## Conclusions


The majority of users in this survey indicated they were already familiar with the extensions they installed in Firefox. The most likely reasons for this are:

* The user got a new computer, and reconfigured Firefox to mirror their old computer.
* The user switched browsers, and reconfigured Firefox to mirror their old browser.

We cannot identify these cases in Telemetry, and so it is imperative that we keep this survey in mind whenever doing analysis on new add-ons users. This survey also suggests that any initiatives to move the needle for new add-on users might be harder than we think, since this segment is overcrowded with add-on users from a past (browser) life. See [this retention analysis](https://metrics.mozilla.com/protected/bmiroglio/addons/retention-change/retention-change.html), which mentions these caveats.





