---
title: "Add-ons (+ Themes) Engagement Study"
author: "Ben Miroglio"
date: "03/20/2018"
output: 
  html_document:
    theme: cosmo
    code_folding: hide
    toc: true
    toc_float: true
---

This document reproduces results from the Firefox Add-ons Engagement Study with the addition of theme data.

**TL;DR**: Installing a theme alone does *not* increase user engagement in the context of this study.


# Background on Study Design

This study involves observational data from Firefox users over 70 days. We segment these days into 3 different periods:

* *Baseline Period*: The first 28 days, restricted to users that do not install an add-on or a theme
* *Treatment Period*: The following 14 days, in which the test group either installs an add-on or a theme
* *Observation Period*: The remaining 28 days, in which we observe behavior for the test and control groups

The control group consists of users that never installed an add-on or a theme in the entire 70 day study.

The idea is that if we control for differences between the test and control groups (via matching techniques) and for their baseline activity (via the baseline period) how does engagement change after a user installs an add-on or a theme? We look at three different Firefox metrics to serve as proxies for engagement:

* **Active Hours**: Mean active hours for a given user per session (mouse clicks, scrolling, key-presses, etc.)
* **Total URIs**: Mean number of webpage loads for a given user per session
* **Search Volume**: Mean number of searches for a given user per session

For more information on the study design and matching process, please refer to the following sources:

* [Add-on Engagement Study Slides](https://docs.google.com/presentation/d/1m6E0LNsB3MfQ5_4lnycjc6IBi7Ty8YOAT__dhWwIqGw/edit#slide=id.g26d133558e_0_1261)
* [The Effect of Ad Blocking on User Engagement with the Web](https://metrics.mozilla.com/protected/bmiroglio/WWW_2018_paper.pdf) (paper to be presented at WWW '18)

-------



```{r, include=F}
library(dplyr)
library(ggplot2)
library(reshape2)
library(data.table)
library(kableExtra)
library(broom)
library(knitr)

# define addons we want to isolate
a1 <- 'addon_.d10d0bf8.f5b5.c8b4.a8b2.2b9879e08c5d.' # Adblock Plus
a2 <- 'addon_uBlock0.raymondhill.net' # uBLock Origin
p1 <- 'addon_.4ED1F68A.5463.4931.9384.8FFF5ED91D92.' # Ghostery
v1 <- 'addon_.b9db16a4.6edc.47ec.a1f4.b86292ed211d.' # Video Download Helper

```




```{r, cache=TRUE, include=F}
# read in matched data
d <- read.csv("./es-data/matched_datafinal.csv")
pv <- c()
setnames(d, old = c("scalar_parent_browser_engagement_tab_open_event_count_post", 
                    "scalar_parent_browser_engagement_total_uri_count_post",
                    "scalar_parent_browser_engagement_unique_domains_count_post"),
            new = c("tab_open_event_count_post", 
                    "total_uri_count_post",
                    "unique_domains_count_post"))

setnames(d, old = c("scalar_parent_browser_engagement_tab_open_event_count", 
                    "scalar_parent_browser_engagement_total_uri_count",
                    "scalar_parent_browser_engagement_unique_domains_count"),
            new = c("tab_open_event_count", 
                    "total_uri_count",
                    "unique_domains_count"))


```



```{r, cache=TRUE, warning=F, include=F}


# these are the measures for which will we estimate an effect
engagementMeasures <- c("active_ticks", "tab_open_event_count", 
                        "total_uri_count", "unique_domains_count",
                        "subsession_length","search_sources_search_bar",
                        "search_sources_url_bar",
                        "search_total",
                        "search_engines_yahoo",
                        "search_engines_google", "places_pages_count", "places_bookmarks_count")

d["log_memory_mb"] = log(d$memory_mb)

code_log <- function(i) ifelse(i > 0, log(i), 0)
for (i in engagementMeasures) {
  log_pre <- paste("log_", i, sep='')
  post <- paste(i, "post", sep="_")
  log_post <- paste("log_", post, sep='')
  is_zero <- paste(i, "is_zero", sep = "_")
  d[log_pre] <- sapply(d[i], code_log)
  if (i!="memory_mb") {
    d[log_post] <- sapply(d[post], code_log)
  }
  d[is_zero] = factor(d[i] == 0)
  
}

# constructs a formula to be fed into lm()
# effect is the treatment binary variable
make.formula <- function(resp, addons=NULL, effect='adblocker') {
  y <- paste("log_", resp, "_post", sep="")
  X <- paste("log_", resp, sep="")
  controllers <- c("n", "log_memory_mb", paste("log", engagementMeasures, sep="_"))
  # if a feature has zero values, add that as a covariate
  if (nrow(unique(d[paste(resp, "is_zero", sep="_")])) > 1) {
    controllers <- c(controllers[which(grepl(resp, controllers) == F)], paste(resp, "is_zero", sep="_"))
}
  # if addons are specified, add them to formula
  # ignoring the treatment variable
  if (!is.null(addons)) {
    X <- paste(X, '+',  paste(addons, collapse = ' + '))
  } else { # add effect
    X <- paste(X, '+', effect)
  }
  X <- paste(X, "+" , paste(controllers, collapse=" + "))
  # cat(paste(y, '~', X))
  formula <- as.formula(paste(y, '~', X))
  formula
}

# returns a list of the top N addons in df
top_addons <- function(df, n) {
  sort(apply(select(df, contains("addon_")), 2, sum), decreasing = TRUE)[1:n]
}

```

```{r, cache=TRUE}
# drop entries where a pre or post measurement is <=0
to_drop <- unique(unlist(sapply(engagementMeasures, function(x) {
  unlist(c(which(d[,x]<0), which(d[,paste(x, "_post", sep='')]<0)))
})))

if (length(to_drop) > 0) {
  d <- d[-to_drop,]
}

# calculate client frequency in dataset, since control profiles
# can be matched to multiple test profiles
a <- aggregate(n~client_id, data=d, length)
colnames(a) <- c("client_id", "weight")


# weight each obs by 1/freq, freq=number of times that client appears in the dataset
model.weights <-  1 / merge(d, a, by="client_id")$weight

# construct bucket for adblockers (AdBlock Plus and uBlock)
d$adblocker<- as.factor(d[a1] + d[a2] >= 1)

# construct variables for Ghostery and Video Download Helper
d$mcafee<- as.factor(d[p1] == 1)
d$video.download <- as.factor(d[v1]  == 1)
d$theme <- as.factor(ifelse(d$install_theme == 'True', 1, 0))
d$addon <- as.factor(ifelse(d$addons_install != '', 1, 0))



# fits linear model with effect as the treatment indicator. Also
# includes all numeric features since we haven't balanced them well after
# matching
# returned object contains summary, residual and qqPlots for both a generic model
# and one that contains the top 10 add-ons. 
fit.model <- function(measure, weights=model.weights, effect="adblocker") {
    f <- make.formula(measure, effect=effect)
    m <- lm(f, data=d, weights=model.weights)
    resid <- m$residuals
    f2 <- make.formula(measure, names(top_addons(d, 10)))
    m2 <- lm(f2, data=d, weights=model.weights)
    resid2 <- m2$residuals
    df = augment(m)
    df2 <- augment(m2)
    p <- ggplot(df, aes(x = .fitted, y = .resid)) + 
      geom_point(size=.2, alpha=.2) + theme_bw() +
      ggtitle("Residuals vs. Fitted Values")
    p2 <- ggplot(df2, aes(x = .fitted, y = .resid)) + 
      geom_point(size=.2, alpha=.2) + theme_bw() +
      ggtitle("Residuals vs. Fitted Values")
    
    p3 <- ggplot(data=data.frame(r=resid), aes(sample=r)) + 
                geom_qq(size=.5, alpha=.2) + theme_bw() + ggtitle("Residual QQ-Plot")
    p4 <- ggplot(data=data.frame(r=resid2), aes(sample=r)) + 
                geom_qq(size=.5, alpha=.2) + theme_bw() + ggtitle("Residual QQ-Plot")
    
    list(summary=summary(m),
         summary2=summary(m2), 
         residPlt=p, 
         residPlt2=p2,
         qqPlot=p3,
         qqPlot2=p4,
         formula=f,
         formula2=f2)

}


```


# Overall Results

The results below isolate the effect of installing

* Any add-on **and** any theme
* Any add-on
* Any theme
* Adblockers (Adblock Plus + uBlock Origin)
* Video Download Helper (`vdh`)
* McAfee Web Advisor (`msa`)


holding all other factors (approximately) equal. These are the 6 treatment groups in question.

Table 1 contains the estimated percent change in each engagement measure after installing an add-on (or theme) that qualifies a user for one or more treatment groups. The plot below the table contains the same information with confidence intervals. 

Note that:

* Any confidence interval that contains zero implies a null effect, and relevant estimates have been changed to 0 in the table.
* Estimates may differ slightly from the original study results, since propensity scores are generated using the added theme data.


```{r, fig.height=7, fig.width=10, warning=F, message=F}
t <- read.csv('overall_results_addon_theme.csv')

tmp <- t
betas <- tmp
betas$group <- factor(betas$group, 
                      levels = c("msa", "vdh", "adblocker", "any_theme",
                                 "any_addon", "addon_and_theme"))
betas <- betas[order(betas$measure, betas$group),]
betas$measure <- factor(betas$measure, 
                        levels=c("Active Hours", "Total URIs", "Search Volume"))


# --------------------------------------------------------
# check if user defined labels have been supplied
# if not, use variable names from data frame
# --------------------------------------------------------
axis.labels <- betas$group
# --------------------------------------------------------
# define sorting criteria. the values on the x-axis are being sorted
# either by beta-values (sort="beta") or by standardized
# beta values (sort = anything else)
# --------------------------------------------------------
# sort labels descending in order of (std.) beta values
# sort rows of data frame descending in order of (std.) beta values
# --------------------------------------------------------
betas <- cbind(xpos = seq_len(nrow(betas)), betas)
betas$p.string <- as.character(betas$ps)
betas$xpos <- as.factor(betas$xpos)
# --------------------------------------------------------
# Calculate axis limits. The range is from lowest lower-CI
# to highest upper-CI, or a user-defined range (if "axis.lim"
# is not NULL)
# --------------------------------------------------------


# --------------------------------------------------------
# Start plot here! First check how to colour geoms
# (whether grouped or not)
# --------------------------------------------------------
y.offset = .39
x.offset = .01
geom.size= 3
vline.type = 2
vline.color = 'red'
axis.title = "title"
legend.title <- "legend title"

betas$estimate_pct <- (exp(betas$estimate) - 1) * 100
betas$conf_low_pct <- (exp(betas$conf.low) - 1) * 100
betas$conf_high_pct <- (exp(betas$conf.high) - 1) * 100

upper_lim <- (ceiling(10 * max(betas$conf_high_pct))) / 10
lower_lim <- (floor(10 * min(betas$conf_low_pct))) / 10

# determine gridbreaks
ticks <- pretty(c(lower_lim, upper_lim))
    
signed <- paste(ifelse(betas$estimate < 0, '', '+'), round(betas$estimate_pct), sep='')
betas$psig <-  paste(paste(signed, '%', sep=''), betas$ps, sep=' ')


di <- data.table(betas)[,.(measure, 
                           group, 
                           pct_change=ifelse(grepl('[*.]', psig), 
                                             gsub('[*.]', '', psig), 
                                             '0%'))]

dc <- dcast(di, measure ~ group)
setcolorder(dc, c('measure', 'addon_and_theme', 
                  'any_addon', 'any_theme', 'adblocker', 
                  'vdh', 'msa'))

dc %>%
  kable('html', 
        caption='Table 1: Estimated Percent Change in Engagement By Treatment Group',
        format.args = list(decimal.mark = '.', big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), 
                full_width=T, font_size=15)
  

betaplot <- ggplot(betas, 
                   aes_string(x='xpos', 
                              y='estimate_pct', 
                              colour='measure', 
                              shape='measure')) +
    # and error bar
    geom_errorbar(aes_string(ymin='conf_low_pct', 
                             ymax='conf_high_pct'), 
                  width = 0) +
    # Print p-values. With vertical adjustment, 
    # so they don't overlap with the errorbars
    geom_text(aes_string(label = "psig"), 
              nudge_x = y.offset,
              show.legend = FALSE, 
              size=3.5) +
    # print point
    geom_point(size = geom.size) +
    # Intercept-line
    geom_hline(yintercept = 0, 
               linetype = vline.type, 
               color = vline.color) +
    # set y-scale-limits, breaks and tick labels
    scale_y_continuous(limits = c(lower_lim, upper_lim), 
                       breaks = ticks, 
                       labels = ticks) +
    # set value labels to x-axis
    scale_x_discrete(labels = axis.labels) + 
    coord_flip() + theme_bw() + theme(legend.position="bottom", 
                                      legend.title=element_blank()) +
    facet_grid(measure ~ ., scales = "free_y") +

    xlab("Treatment Group") + ylab("Estimate") + 
    labs(title='Estimated Percent Change in Engagement (w 95% Confidence Intervals) By Treatment',
         subtitle="Significance codes    0: ***,  0.001: **,  0.01: *,  0.05: . ")
 

betaplot

```

### Interpretation

Since we allow a 28 day baseline period, users in the test group can be thought of as users that "discovered" add-ons or themes, since they exibited significant behavior without add-ons or themes for at least 28 days.

Looking at Table 1 we can say the following:

* For users that "discover" add-ons *and* themes, we expect their active hours, total URIs, and search volume to change by +12%, +9% and 0% respectively.
* For users that "discover" add-ons, we expect their active hours, total URIs, and search volume to change by +8%, +9% and -12% respectively.
* For users that "discover" themes, we expect to see no change in active hours, total uris and search volume (all being 0%).



-----


# Model-By-Model Results {.tabset}

This section is for the curious. The key takeaways have been summarized above.

## Add-ons AND Themes {.tabset}
```{R}
t <- data.frame()
d$addons_themes <- ifelse(d$addon == 1 & d$theme == 1, 1, 0)
cat("Number of users with add-ons AND themes:", sum(ifelse(d$addons_themes == 1, 1, 0)))

```


### Active Ticks 


```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
options(width=120)
f <- fit.model("active_ticks", effect='addons_themes')
f$summary

ggplot(data=d) + 
        geom_point(aes(x=log(active_ticks), y=log(active_ticks_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='addon_and_theme=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='addon_and_theme=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()


p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)


```





### Total URIs 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("total_uri_count", effect="addons_themes")
f$summary



ggplot(data=d) + 
        geom_point(aes(x=log(total_uri_count), y=log(total_uri_count_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='addon_and_theme=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='addon_and_theme=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot


fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)

```



### Search Total 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("search_total", effect="addons_themes")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(search_total), y=log(search_total_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='addon_and_theme=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='addon_and_theme=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])
#grid.arrange(p1, p2)
```





## General Add-ons {.tabset}
```{R}
cat("Number of users with add-ons:", sum(ifelse(d$addon==1, 1, 0)))


```


### Active Ticks 


```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
options(width=120)
f <- fit.model("active_ticks", effect='addon')
f$summary

ggplot(data=d) + 
        geom_point(aes(x=log(active_ticks), y=log(active_ticks_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='addon=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='addon=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()


p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)


```





### Total URIs 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("total_uri_count", effect="addon")
f$summary



ggplot(data=d) + 
        geom_point(aes(x=log(total_uri_count), y=log(total_uri_count_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='addon=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='addon=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot


fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)

```



### Search Total 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("search_total", effect="addon")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(search_total), y=log(search_total_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='addon=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='addon=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])
#grid.arrange(p1, p2)
```

## General Themes {.tabset}
```{R}
cat("Number of users with themes:", sum(ifelse(d$theme==1, 1, 0)))
```


### Active Ticks 


```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
options(width=120)
f <- fit.model("active_ticks", effect='theme')
f$summary

ggplot(data=d) + 
        geom_point(aes(x=log(active_ticks), y=log(active_ticks_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='theme=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='theme=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()


p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)


```





### Total URIs 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("total_uri_count", effect="theme")
f$summary



ggplot(data=d) + 
        geom_point(aes(x=log(total_uri_count), y=log(total_uri_count_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='theme=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='theme=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot


fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)

```



### Search Total 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("search_total", effect="theme")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(search_total), y=log(search_total_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='theme=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='theme=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])
#grid.arrange(p1, p2)
```




## Adblockers {.tabset}

```{R}
cat("Number of users with adblockers (uBlock + ABP):", sum(ifelse(d$adblocker==T, 1, 0)))

```
### Active Ticks 


```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
options(width=120)
f <- fit.model("active_ticks")
f$summary

ggplot(data=d) + 
        geom_point(aes(x=log(active_ticks), y=log(active_ticks_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='adblocker=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='adblocker=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()


p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)


```









### Total URIs 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("total_uri_count")
f$summary



ggplot(data=d) + 
        geom_point(aes(x=log(total_uri_count), y=log(total_uri_count_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='adblocker=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='adblocker=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot


fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)

```



### Search Total 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("search_total")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(search_total), y=log(search_total_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='adblocker=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='adblocker=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])
#grid.arrange(p1, p2)
```





## Video Download Helper {.tabset}

```{R}
cat("Number of users with VDH:", sum(ifelse(d$video.download==T, 1, 0)))
```
### Active Ticks 


```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
options(width=120)
f <- fit.model("active_ticks", effect="video.download")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(active_ticks), y=log(active_ticks_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='video.download=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='video.download=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()


p1 <- f$residPlt
p2 <- f$qqPlot


fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])
#grid.arrange(p1, p2)


```








### Total URIs 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("total_uri_count", effect="video.download")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(total_uri_count), y=log(total_uri_count_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='video.download=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='video.downloadr=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)

```


### Search Total 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("search_total", effect="video.download")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(search_total), y=log(search_total_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='video.download=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='video.download=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot
fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]

t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)
```







## McAfee Web Advisor {.tabset}

```{R}
cat("Number of users with mcafee:", sum(ifelse(d$mcafee==T, 1, 0)))
```
### Active Ticks 


```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
options(width=120)
f <- fit.model("active_ticks", effect="mcafee")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(active_ticks), y=log(active_ticks_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='mcafee=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='mcafee=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()


p1 <- f$residPlt
p2 <- f$qqPlot

fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])

#grid.arrange(p1, p2)


```






### Total URIs 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("total_uri_count", effect="mcafee")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(total_uri_count), y=log(total_uri_count_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='mcafee=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='mcafee=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot
fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])
#grid.arrange(p1, p2)

```



### Search Total 



```{r, warning=F, message=F, fig.height=8, fig.width=8, cache=TRUE}
f <- fit.model("search_total", effect="mcafee")
f$summary


ggplot(data=d) + 
        geom_point(aes(x=log(search_total), y=log(search_total_post), 
                       colour="points"), color="black", alpha=.2, size=.2) +
        geom_abline(aes(color='mcafee=1', 
                        intercept=f$summary$coefficients[1,1] + 
                                  f$summary$coefficients[3,1], 
                        slope=f$summary$coefficients[2,1])) +
        geom_abline(aes(color='mcafee=0', 
                        intercept=f$summary$coefficients[1,1],  
                        slope=f$summary$coefficients[2,1])) +
              ggtitle("Fitted Regression Lines") +
  scale_colour_discrete("Treatment") + theme_bw()

p1 <- f$residPlt
p2 <- f$qqPlot
fit <- lm(f$formula, data=d)

tmp <- broom::tidy(fit, conf.int = TRUE) %>%
    dplyr::slice(-1) %>%
    dplyr::select_("term", "estimate", "conf.low", "conf.high")

c <- tmp[2,]
t <- rbind(t, c)
pv <- c(pv, f$summary$coefficients[3,4])
#grid.arrange(p1, p2)
```






```{r}
t$pv <- pv
t$term <- c(rep('addon_and_theme', 3), rep("any_addon", 3), rep("any_theme", 3), rep("adblocker", 3), rep("vdh", 3), rep("msa", 3))
t$measure <- rep(c("Active Hours", "Total URIs", "Search Volume"), 6)
t$group <- t$term
t$ps <- sapply(t$pv, function(i) {
  if (i < 0.00001) '***'
  else if (i < 0.001) '**'
  else if (i < 0.01) '*'
  else if (i < 0.05) '.'
  else ' '
})
t

write.csv(t, "overall_results_addon_theme.csv")


```










